---
title: "Annan and Blattman Matching Example"
author: "Chad Hazlett"
date: "16 April 2020"
output: html_document
---

Code for Annan and Blattman Piece on Effects of Abduction, with Matching

```{r}
library(foreign)
library(Matching)
library(ebal)

dat=read.csv("BlattmanAnnan.csv")

head(dat)
```

# MATCHING
## Check the covariate balance in the unmatched dataset. 

First, before reporting actual balance statistics let's take a look at what seems to predict treatment status:

```{r}
summary(lm(abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+
             C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal,data=dat))
```

Second, we could check balance "by hand". For example, on age:
```{r}
t.test(dat$age~dat$abd, var.equal=FALSE)
ks.test(x=dat$age[dat$abd==1], y=dat$age[dat$abd==0])
plot(ecdf(dat$age[dat$abd==1]),verticals=TRUE,col=2,cex=0,main="eCDFs of Age by Abduction Status")
par(new=TRUE)
plot(ecdf(dat$age[dat$abd==0]),verticals=TRUE,col=1,cex=0,main="")
legend("topleft",lty=c(1,1), c("Treated","Control"),col=c(2,1))
```

Confirm with density plots
```{r, fig.width=6, fig.height=4}
plot(density(dat$age[dat$abd==1]),ylim=c(0,0.1),col=2,cex=0,main="PDF of Age by Abduction Status")
lines(density(dat$age[dat$abd==0]),col=1,cex=0,main="")
legend("topright",lty=c(1,1),c("Treated","Control"),col=c(2,1))
```

Often you'll want to speed up the process, so use MatchBalance. With just a few covars first, to make it easy to see:

```{r}
library(Matching)
mb = MatchBalance(abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+
                  C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal,data=dat, nboots=10000)

varnames=c("age","fthr_ed","mthr_ed","hh_size96","orphan96",
           "C_ach","C_akw","C_ata","C_kma","C_oro","C_pad","C_paj","C_pal")
```

That's pretty ugly. Useful to collect these results via `baltest.colect`, in the `ebal` package:

```{r}
library(ebal)
btest=baltest.collect(mb,var.names=varnames,after=F)

#Display output, rounding to two digits
round(btest,3)

round(btest[,c("mean.Tr","mean.Co","T pval","KS pval")],2)
```

# Matching

Select covariates to match on in order to identify the ATT, according to our identification assumptions.  Together with others you may want to get balance on. Let's use one match per treated unit, with replacement.

First just some organizing:
```{r}
varnames=c("age","fthr_ed","mthr_ed","hh_size96","orphan96",
           "C_ach","C_akw","C_ata","C_kma","C_oro","C_pad","C_paj","C_pal")

exactmatch=c(FALSE,TRUE,TRUE,FALSE,TRUE, replicate(8,"TRUE")) 
X=dat[,varnames]
```

Now the actual matching:
```{r}
matchout1=Match(Y=dat$educ, Tr=dat$abd, X=X, M=1,exact=exactmatch,estimand="ATT")
#with bias adjustment
matchout2=Match(BiasAdjust=TRUE,Y=dat$educ, Tr=dat$abd, X=X, M=1, exact=exactmatch,estimand="ATT")
```

Ordinarily we'd check balance before proceeding, but let's stop to see what actually in this object.

```{r}
ls(matchout1)
summary(matchout1)
matchout1$est
matchout1$se #Abadie Imbens SE
length(matchout1$index.treated)
length(matchout1$index.control)
length(unique(matchout1$index.control))
```

And with the bias-adjusted estimates:
```{r}
matchout2$est
matchout2$se
```

Compare to "naive" estimate:

```{r}
summary(lm(dat$educ~dat$abd))
```

## Balance After Matching
Normally, before you even look at results you'd examine balance post-matching. Note, you can check balance on things that weren't matched on to make sure they got balanced too. 

```{r}
mb.after = MatchBalance(match.out=matchout1,abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal,data=dat, print.level = 0, nboots=10000)

btest_after=baltest.collect(mb.after,var.names=varnames,after=TRUE)

#Display output, rounding to two digits
round(btest_after[,c("mean.Tr","mean.Co","T pval","KS pval")],2)
```

Let's see the balance before and after, next to each other:
```{r}
#See balance before and after next to each other
balancecompare=cbind(round(btest[,c("mean.Tr","mean.Co","T pval","KS pval")],3),round(btest_after[,c("mean.Tr","mean.Co","T pval","KS pval")],3))

balancecompare
```

# Balance with Covariate-Balancing Weights

We could instead choose weights on the control units s.t. the weighted average of each $X$ for the controls equals the (unweighted) average among the treated. We could similarly get weighted average of each $X^2$ to match up, etc.  So this gives exact balance, though only on enumerated moments. 

```{r}
library(ebal)
#remove one location dummy
X.ebal=X[,-13]
varnames.ebal=varnames[-13]
eb.out = ebalance(dat$abd, X=X.ebal)
```

That only gives weights for controls; I'd like an N-dim vector with all weights:
```{r}
ebalw=replicate(length(dat$abd),1)
ebalw[dat$abd==0]=eb.out$w
```

Let's see how it does on improving the balance. 

```{r}
bout.ebal=MatchBalance(dat$abd~as.matrix(X),weights=ebalw, print.level=0, nboots=10000)
bal.ebal=baltest.collect(matchbal.out=bout.ebal,var.names=colnames(X),after=F)

balancecompare.ebal=cbind(round(btest[,c("mean.Tr","mean.Co","T pval","KS pval")],2), round(bal.ebal[,c("mean.Tr","mean.Co","T pval","KS pval")],2))

balancecompare.ebal

```

Note KS test on age and household size....actually the KS test invoked by `MatchBalance` *fails with weights*, so don't trust these.

Now let's plot the standardized imbalance:

```{r}
d=rbind(as.matrix(btest[,4]),as.matrix(bal.ebal[,4]))
d.vnames=rownames(d)
rownames(d)=NULL
colnames(d)="sdiff.pooled"
d=data.frame(d)
d$vname <- d.vnames
d$vname <- factor(d$vname,levels = unique(d$vname)[ncol(X):1], labels = unique(d$vname)[ncol(X):1])
d$gr <- rep(c("orig","ebal"),each=ncol(X))
library(lattice)
library(RColorBrewer)
Cex <- 1.2
Cex2 <- 1
mypal<-brewer.pal(3,"Set2")
#pdf("ebal_blattman.pdf", heigh=4, width=6)
print(
  xyplot(vname~sdiff.pooled/100,data=d,groups=gr,
         xlim=c(-2,2),
         panel = function(x,y,...)
         {
           panel.abline(v=0, lwd = 1 , lty="solid")
           panel.abline(v=c(-2,-1,1,2), lwd = 2 , lty="dotted")
           panel.abline(h=c(1:nrow(d)), lwd = 1 , lty="dashed", col="gray95")
           panel.xyplot(x,y,...)
         }
         ,par.settings = list(superpose.symbol = list(pch = c(15,18,19),col=mypal,cex=1.2))
         ,xlab=list("standardized difference in means",cex=Cex),ylab="",auto.key=T,scales=list(y=list(cex=Cex),x=list(cex=Cex2,at=c(-1,-.5,0,.5,1),labels=c("-1","-.5","0",".5","1")))
  )
)

dev.off()
```

# Propensity Scores

Another approach is to estimate propensity scores, then either match on them or use IPW weights.  Let's get the scores first, by a simple model:

```{r}
pi.out = glm(abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal,data=dat, family="binomial"(link=logit))
```

How do they look for treated and control?
```{r}
#pdf("pscores_pre.pdf", height=4, width=6)
plot(density(pi.out$fit[dat$abd==1]), lwd=2, main="Distribution of pscores")
lines(density(pi.out$fit[dat$abd==0]), lwd=2, lty=2)
legend("topleft", legend=c("treated","controls"), lty=c(1,2), lwd=2)
#dev.off()
```

One way to use this is to simply match on the propensity score as if it was the (only) covariate.

```{r}
matchout.pi=Match(Y=dat$educ, Tr=dat$abd, X=pi.out$fit, M=1,estimand="ATT")
summary(matchout.pi)
```

Check balance:

```{r}
mb.out.pi = MatchBalance(match.out=matchout.pi,abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal,data=dat, print.level=0)

btest_after_pi=baltest.collect(mb.out.pi,var.names=varnames,after=TRUE)

#See balance before and after next to each other
balancecompare.pi=cbind(round(btest[,c("mean.Tr","mean.Co","T pval","KS pval")],2), round(btest_after[,c("mean.Tr","mean.Co","T pval","KS pval")],2), round(btest_after_pi[,c("mean.Tr","mean.Co","T pval","KS pval")],2))

balancecompare.pi
```

```{r}
###-----------------------------------------------
### Now with stabilized IPW weights:
###----------------------------------------------
ps=pi.out$fit
D=dat$abd
PrD=mean(D)
IPW= (D*PrD+(1-D)*(1-PrD))/(D*ps+(1-D)*(1-ps))
```

```{r}
plot(density(IPW), main="Density of IPW weights")
```

See how distribution of pscores has changed:
```{r}
plot(density(pi.out$fit[D==1], weight=IPW[D==1]/sum(IPW[D==1])), lwd=2, main="Distribution of pscores: Weighted")
lines(density(pi.out$fit[D==0], weight=IPW[D==0]/sum(IPW[D==0])),lwd=2, lty=2)
legend("topleft", legend=c("treated","controls"), lty=c(1,2), lwd=2)
```

Check omnibus balance:
```{r}
omnibus.bal = lm(abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+
                   C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal, data=dat) 
summary(omnibus.bal)

omnibus.bal.ipw = lm(abd~age+fthr_ed+mthr_ed+hh_size96+orphan96+
                   C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal, 
                   weight=IPW, data=dat) 
summary(omnibus.bal.ipw)  #yay!
```

Now use weights in regression:
```{r}
lm.out.naive = lm(educ~abd, data=dat) 
summary(lm.out.naive)

lm.out.ipw = lm(educ~abd, weight=IPW, data=dat) 
summary(lm.out.ipw)
```

Adding covariates should not change estimate on "abd":
```{r}
lm.out.ipw2 = lm(educ~abd+age+fthr_ed+mthr_ed+hh_size96+orphan96+
                  C_ach+C_akw+C_ata+C_kma+C_oro+C_pad+C_paj+C_pal, weight=IPW, data=dat) 
summary(lm.out.ipw2)
```

Let's plot balance again with a few more results. First get balance from IPW weighting

```{r}
bout.ipw=MatchBalance(dat$abd~as.matrix(X),weights=IPW)
bal.ipw=baltest.collect(matchbal.out=bout.ipw,var.names=colnames(X),after=F)

#Let's plot the standardized imbalance:
d=rbind(as.matrix(btest[,4]),as.matrix(bal.ebal[,4]), 
        as.matrix(bal.ipw[,4]), as.matrix(btest_after_pi[,4]))
#d=rbind(as.matrix(bal.kbal[,4]),as.matrix(bal.match[,4]))
d.vnames=rownames(d)
rownames(d)=NULL
colnames(d)="sdiff.pooled"
d=data.frame(d)
d$vname=d.vnames
d$vname <- factor(d$vname,levels = unique(d$vname)[ncol(X):1], labels = unique(d$vname)[ncol(X):1])
d$gr <- rep(c("orig","ebal","ipw","psmatch"),each=ncol(X))

library(lattice)
library(RColorBrewer)
Cex <- 1.2
Cex2 <- 1

mypal<-brewer.pal(4,"Set2")

#pdf("all_blattman.pdf", height=6, width=8)
print(
  
  xyplot(vname~sdiff.pooled/100,data=d,groups=gr,
         #xlim=c(min(d$sdiff.pooled/100),max(d$sdiff.pooled/100)),
         xlim=c(-1.1,1.1),
         panel = function(x,y,...)
         {
           panel.abline(v=0, lwd = 1 , lty="solid")
           panel.abline(v=c(-1,-.5,.5,1), lwd = 2 , lty="dotted")
           panel.abline(h=c(1:nrow(d)), lwd = 1 , lty="dashed", col="gray95")
           #panel.grid(v=0,h=-1)
           panel.xyplot(x,y,...)
         }
         ,par.settings = list(superpose.symbol = list(pch = c(1,15,16,17),col=mypal,cex=1.5))
         #,par.settings = list(superpose.symbol = list(pch = c(15,18,19),col=mypal,cex=1.2))
         ,xlab=list("standardized difference in means",cex=Cex),ylab="",auto.key=T,scales=list(y=list(cex=Cex),x=list(cex=Cex2,at=c(-1,-.5,0,.5,1),labels=c("-1","-.5","0",".5","1")))
  )
)
```

